---
title: Quarterly report
output: html_document
params:
  division: NA
  directorate: NA
  team: NA
  date_from: NA
  date_to: NA
  carerSU: NA
  area_name: NA
---

<!-- So I need to declare the parameters here, and then pass them through from Shiny -->
<!-- Then I can use an observe() function with the GET string so the report is generated if -->
<!-- The parameters are set using a GET string -->

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)

# calculate the date range first

today = Sys.Date()

previous_quarter <- (quarter(today)) - 1 %% 4
previous_year <- year(today)

if(previous_quarter == 0){
  
  previous_quarter <- 4
  previous_year <- previous_year - 1
}

first_date <- yq(paste0(previous_year, ": Q", previous_quarter))

end_date <- yq(paste0(year(today), ": Q", quarter(today))) - 1

# filter by area and name the areas

if(params$division != "NA"){
  
  suceData = trustData %>%
    filter(Division %in% params$division)
  
} else if(params$directorate != "NA"){
  
  suceData = trustData %>%
    filter(Directorate %in% params$directorate)
  
} else if(params$team != "NA"){
  
  suceData = trustData %>%
    filter(TeamC %in% params$team)
} else {
  
  suceData = trustData
}

# now filter by SU/ carer

if(params$carerSU == "SU"){
  
  suceData = suceData %>%
    filter(is.na(formtype) | formtype != "SUCE")
  
} else if(params$carerSU == "carer"){
  
  suceData = suceData %>%
    filter(formtype == "carer")
  
} else if(params$carerSU == "bothCarerSU"){
  
  # nothing!
}

# filter by time last and produce another dataset with 2 years in

two_year_data <- suceData %>% 
  filter(Date > end_date - 365 * 2)

suceData <- suceData %>% 
  filter(Date >= first_date, Date <= end_date)

# generate report information

if(is.null(suceData)){
  
  report_information = NULL
  
} else {
  
  # FFT score
  
  promoterScores = suceData[, "Promoter2"]
  
  if(length(promoterScores[!is.na(promoterScores)]) > 0) {
    
    FFT = round(sum(promoterScores %in% 4:5, na.rm = TRUE) /
                  sum(promoterScores %in% 0:5, na.rm = TRUE) * 100, 0)
    
  }
  
  # Quality score
  
  SQ = round(mean(suceData[, "Service"], na.rm = TRUE) * 20, 0)
  
  # Number of responses
  
  NR = nrow(suceData)
  
  NSQ = length(suceData$Service[!is.na(suceData$Service)])
  
  NFFT = length(suceData$Promoter2[!is.na(suceData$Promoter2)])
  
  # number of comments
  
  IC = length(suceData[, "Improve"][!is.na(suceData[, "Improve"])])
  BC = length(suceData[, "Best"][!is.na(suceData[, "Best"])])
  
  # were you aware of how to raise a concern yes/ no/ maybe
  
  complaint_numbers <- map_int(c("D", "N", "Y"), function(x){
    
    suceData %>%
      filter(Complaint == x) %>%
      nrow()
  })
  
  # criticality
  
  improve_numbers <- map_int(c(1, 2, 3), function(x){
    
    suceData %>%
      filter(ImpCrit == x) %>%
      nrow()
  })
  
  # criticality
  
  best_numbers <- map_int(c(1, 2, 3), function(x){
    
    suceData %>%
      filter(BestCrit == x) %>%
      nrow()
  })
  
  report_information <- 
    list("theArea" = params$area_name, "NR" = NR, "IC" = IC, "BC" = BC, "NFFT" = NFFT,
         "FFT" = FFT, "NSQ" = NSQ, "SQ" = SQ, "complaint_numbers" = complaint_numbers,
         "improve_numbers" = improve_numbers, "best_numbers" = best_numbers)
}

```

<!-- ## Context -->

```{r}

# what I need more than anything here is a list of the other report areas so I can link 

# fetch the state of the teams

```

## Summary

This report summarises data from `r first_date` to `r end_date`

```{r, results = "asis"}

if(is.null(report_information)){
  
  myString = "Within the selected time and area there were no responses"
} else {
  
  myString = paste0("<p>Within ", report_information[["theArea"]], " in the selected time there were ", report_information[["NR"]],
                    " responses.</p><br>",
                    "<p>There were ", report_information[["IC"]], " 'What could we do better' responses and ", report_information[["BC"]],
                    " 'What did we do well' responses</p><br>",
                    ifelse(report_information[["NFFT"]] > 9,
                           paste0("<p>The Friends and Family Test Score is the proportion of patients
      who are extremely likely or likely to recommend a service. In the selected period of time it was ",
      report_information[["FFT"]], "% (based on ", report_information[["NFFT"]], " responses.)", "</p><br>"), ""),
      ifelse(report_information[["NSQ"]] > 9,
             paste0("<p>Service quality rating was ", report_information[["SQ"]], 
                    "% (based on ", report_information[["NSQ"]],
                    " responses.)</p>"), ""),
      ifelse(sum(report_information[["complaint_numbers"]]) > 3,
             paste0("<p>", report_information[["complaint_numbers"]][3], 
                    " individuals reported that they knew how to make a complaint, ",
                    report_information[["complaint_numbers"]][2], 
                    " reported that they did not know how to make a complaint, and ",
                    report_information[["complaint_numbers"]][1], 
                    " reported that they were unsure if they knew.</p>"), "")
  )
}

cat(myString)

```

## Summary of responses

```{r}

theQuestions = c("Service", "Promoter", "Listening", "Communication", "Respect", "Positive")

# remove decimals from historic data

fixedData = data.frame(apply(suceData[, theQuestions], 1:2,
                             function(x) round(x + .01)))

# count the missing responses

missnum = apply(fixedData, 2, function(x) sum(!is.na(x)))

if(length(names(missnum[missnum > 2])) < 3){
  
  return(NULL)
}

fixedData[, missnum > 2] %>%
  gather(L1, value) %>% 
  filter(!is.na(value)) %>%
  left_join(select(questionFrame, code, value), by = c("L1" = "code")) %>%
  select(-L1) %>%
  group_by(value.y) %>%
  count(value.x) %>%
  mutate(prop = prop.table(n) * 100) %>%
  filter(!is.na(prop)) %>% 
  ungroup() %>%
  ggplot(aes(x = value.y, y = prop, fill = factor(value.x))) +
  geom_bar(position = "fill", stat = "identity") + ylab("Proportion responding") + 
  scale_fill_manual(values = rainbow(5), "Response", limits = c(1:5), breaks = c(5:1),
                    labels = c("Excellent", "Good", "Fair", "Poor", "Very poor")) +
  scale_y_continuous(labels = percent_format()) +
  guides(fill = guide_legend(reverse = TRUE)) + 
  scale_x_discrete() + coord_flip() + xlab("Question")


```

```{r}

theQuestions = c("Service", "Promoter", "Listening", "Communication", "Respect", "Positive")

sample_data <- two_year_data

sample_data$Quarter = yq(paste0(year(sample_data$Date), ": Q", quarter(sample_data$Date)))

mean_score <- sample_data %>% 
  select(c("Quarter", "Service", "Promoter", "Listening", "Communication", "Respect", "Positive")) %>% 
  group_by(Quarter) %>% 
  summarise_if(is.numeric, function(x) mean(x, na.rm = TRUE) * 20)

minimum_value = mean_score %>% 
  select(c("Service", "Promoter", "Listening", "Communication", "Respect", "Positive")) %>% 
  min(na.rm = TRUE) %>% 
  `-`(20)

number_scores <- sample_data %>% 
  select(c("Quarter", "Service", "Promoter", "Listening", "Communication", "Respect", "Positive")) %>% 
  group_by(Quarter) %>% 
  summarise_all(function(x) length(x[!is.na(x)]))

mean_score[number_scores < 3] = NA

mean_score %>% 
  gather(Question, value, -Quarter) %>% 
  ggplot(aes(x = Quarter, y = value, group = Question, colour = Question)) +
  geom_line() + 
  geom_point() +
  ylim(minimum_value, 100) 

```

## What could we do better?

```{r, results = "asis"}

# produce all the variables and then place them inline below the chunk

returnTopComments <- function(nth_row, type){
  
  if(type == "Improve"){
    
    check1 <- suceData %>% 
      filter(!is.na(Imp1)) %>% 
      left_join(categoriesTable, by = c("Imp1" = "Number")) %>% 
      select(Category, Super)
    
    check2 <- suceData %>% 
      filter(!is.na(Imp2)) %>% 
      left_join(categoriesTable, by = c("Imp2" = "Number")) %>% 
      select(Category, Super)
  }
  
  if(type == "Best"){
    
    check1 <- suceData %>% 
      filter(!is.na(Best1)) %>% 
      left_join(categoriesTable, by = c("Best1" = "Number")) %>% 
      select(Category, Super)
    
    check2 <- suceData %>% 
      filter(!is.na(Best2)) %>% 
      left_join(categoriesTable, by = c("Best2" = "Number")) %>% 
      select(Category, Super)
  }
  
  check_final <- rbind(check1, check2)
  
  count_table <- check_final %>% 
    filter(!is.na(Super), !is.na(Category)) %>% 
    group_by(Category, Super) %>% 
    count() %>% 
    ungroup()
  
  # this is the bit that returns the nth top comment
  
  return_table <- count_table %>% 
    mutate(percent = round(n / sum(n) * 100, 1)) %>% 
    arrange(-percent) %>% 
    slice(nth_row)
  
  # return three comments that are exemplars of that comment
  
  comment_numbers <- return_table %>% 
    left_join(categoriesTable, by = c("Category", "Super")) %>% 
    pull(Number)
  
  if(type == "Improve"){
    
    return_comments <- suceData %>% 
      filter(Imp1 %in% comment_numbers |
               Imp2 %in% comment_numbers) %>% 
      filter(!is.na(Improve)) %>% 
      sample_n(ifelse(nrow(.) >= 3, 3, nrow(.))) %>%  
      pull(Improve) %>% 
      paste0("<p>", 1 : length(.), ": ", ., "</p>", collapse = "")
  }
  
  if(type == "Best"){
    
    return_comments <- suceData %>% 
      filter(Best1 %in% comment_numbers |
               Best2 %in% comment_numbers) %>% 
      filter(!is.na(Best)) %>% 
      sample_n(ifelse(nrow(.) >= 3, 3, nrow(.))) %>%  
      pull(Best) %>% 
      paste0("<p>", 1 : length(.), ": ", ., "</p>", collapse = "")
  }
  
  return(list("return_table" = return_table, 
              "return_comments" = return_comments))
}

improve_1 <- returnTopComments(1, "Improve")[["return_table"]]
improve_2 <- returnTopComments(2, "Improve")[["return_table"]]
improve_3 <- returnTopComments(3, "Improve")[["return_table"]]

```

The most common comment category was `r paste0(improve_1$Super, ": ", improve_1$Category)` (`r paste0(improve_1$percent, "%")`). Example comments include:

`r returnTopComments(1, "Improve")[["return_comments"]]`

The second most common comment category was `r paste0(improve_2$Super, ": ", improve_2$Category)` (`r paste0(improve_2$percent, "%")`). Example comments include:

`r returnTopComments(2, "Improve")[["return_comments"]]`

The third most common comment category was `r paste0(improve_3$Super, ": ", improve_3$Category)` (`r paste0(improve_3$percent, "%")`). Example comments include:

`r returnTopComments(3, "Improve")[["return_comments"]]`

## What did we do well?

```{r, results = "asis"}

best_1 <- returnTopComments(1, "Best")[["return_table"]]
best_2 <- returnTopComments(2, "Best")[["return_table"]]
best_3 <- returnTopComments(3, "Best")[["return_table"]]

```

The most common comment category was `r paste0(best_1$Super, ": ", best_1$Category)` (`r paste0(best_1$percent, "%")`). Example comments include:

`r returnTopComments(1, "Best")[["return_comments"]]`

The second most common comment category was `r paste0(best_2$Super, ": ", best_2$Category)` (`r paste0(best_2$percent, "%")`). Example comments include:

`r returnTopComments(2, "Best")[["return_comments"]]`

The second most common comment category was `r paste0(best_3$Super, ": ", best_3$Category)` (`r paste0(best_3$percent, "%")`). Example comments include:

`r returnTopComments(3, "Best")[["return_comments"]]`